\mytitle

### 2016-11-01 pdocs/thesis/article.tex
acm tog styling of article continues

% Simo.Nikula@gmail.com
\def\mytitle{Elastic-plastic Constraint for Rigid Body Simulation}
\def\lut{Lappeenranta University of Technology}
\def\bullet{Bullet Physics}
\def\demolisher{DemolisherDemo}
\def\charpy{CharpyDemo}
\def\myvolume{VV}
\def\mynumber{N}
\def\myyear{YYYY}
\def\mymonth{Month}
\def\myaan{XXX}
\def\mydoi{XXXXXXX.YYYYYYY}

\documentclass{acmtog}
\acmVolume{\myvolume}
\acmNumber{\mynumber}
\acmYear{\myyear}
\acmMonth{\mymon}
\acmArticleNum{\myaan}  
\acmdoi{10.1145/\mydoi}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
%\usepackage{natbib}
%\usepackage{lastpage}   % page count
%\usepackage{amsmath}
\usepackage{listings}
% \usepackage{mathdots}  % improved \ddots and \iidots
%\usepackage{amssymb}
%\usepackage[english]{babel}
%\usepackage[intoc]{nomencl} % including table of content
%\usepackage{ifthen}
%\usepackage[hmargin=2.0cm,vmargin=1.6cm]{geometry} % setting marginals
%\usepackage{fancyhdr,extramarks}  % header ja footer manipulation
%\usepackage{times}  % to change font to times
%\usepackage{setspace} % for linespacingx
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usepackage{caption}
\usepackage{varwidth}
\usepackage{enumitem} % 
\begin{document}

\title{\mytitle}
markboth{S. Nikula et al.}{\mytitle}

@@

\acmformat{Nikula, S., Mikkola, A., Björk, T.,  G. V. G. \myyear. 
\mytitle.  {ACM Trans. Graph.} \myvolume, \mynumber, Article \myaan (\mymon \myyear), # pages.\newline  DOI $=$
10.1145/\mydoi\newline http://doi.acm.org/10.1145/\mydoi}

@@

Authors' addresses: Simo.Nikula@gmail.com
\end{bottomstuff}

\include{article-introduction}
\include{article-section-2}
\include{article-section-3}
\include{article-conclusion}

>>>>

% Simo.Nikula@gmail.com
\def\mytitle{Elastic-plastic Constraint for Rigid Body Simulation}
\def\lut{Lappeenranta University of Technology}
\def\bullet{Bullet Physics}
\def\demolisher{DemolisherDemo}
\def\charpy{CharpyDemo}

\documentclass{acmtog}
\acmVolume{VV}
\acmNumber{N}
\acmYear{201Y}
\acmMonth{Month}
\acmArticleNum{AN}  
\acmdoi{10.1145/xxx.yy}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usepackage{varwidth}
\usepackage{enumitem} % 
\begin{document}
\markboth{S. Nikula, A. Mikkola and T. Björk}{\mytitle}

@@

\acmformat{Nikula, S., Mikkola, A., Björk, T.,  G. V. G. 201x. 
\mytitle.  {ACM Trans. Graph.} VV, NN, Article AN (Mon 201x), nb pages.\newline  DOI $=$
10.1145/xx.yy\newline http://doi.acm.org/10.1145/XXXXXXX.YYYYYYY}

@@

%Authors' addresses: Simo.Nikula@gmail.com
\end{bottomstuff}

\input{article-introduction}
\input{article-section-2}
\input{article-section-3}
\input{article-conclusion}
